Intended Table of Contents Thesis

### 2013-03-20 Chapters/Chapter1/paper_list.tex
Temporal segmentation

*****

@@

>>>>

@@

\subsubsection{Pure segmentation}
\begin{itemize}
  \item ``Bayesian Online Changepoint Detection'', \cite{adams2007bayesian}, cited: 67, 2007. Uses a priori and posteriori distribution prediction of the current run-length. Online. Uses well-drilling data, Dow Jones return value and coal-mine accidents rate, which are all used by others. Does not compare results. Decouples algorithm from model (?).
  \item CUSUM Method: piece wise segments of gaussian mean with noise. More refs needed.
  \item ``An Automatic Segmentation Technique in Body Sensor Networks based on Signal Energy'', \cite{guenterberg2009automatic}, cited: 13. Automatic segmenting, adaptive threshold. Pure segmenting, no classification. Nice and clean method? Weakness: single action segmented as multiple. Used multiple sensors.
  \item ``Segmenting Motion Capture Data into Distinct Behaviors'', \cite{barbivc2004segmenting}, cited: 242, 2004. On-line methods: cut-points on increased intrinsic dimensionality, distribution of poses is observed to change. Batch: cut when consecutive frames belong to different Gaussian mixture models. Fixed fourteen motions, compared with manual segmentation. Uses PCA and Probabilistic PCA (models the non-pc subspaces as noise). PPCA is the best. (paper anne)
\end{itemize}
